Palomar 5 Gaps

### 2024-10-28 paper/main.tex
another touch up

  Previous studies have predominantly focused on the creation of gaps in stellar streams due to dark matter subhalo passages, with some exceptions that considered giant molecular clouds. If globular clusters can indeed create such gaps, this factor must be taken into account when using stellar streams to infer the population of dark matter subhaloes. In our study, we focus on Palomar 5, one of the most extensively studied and well-constrained globular cluster streams, known for its ease of observation. We present a result from one of our simulations in Fig. \ref{fig:stream_on_sky}. The following sections detail our modeling of the stream, its gravitational interactions with the galaxy and other globular clusters, and the statistical analysis of perturbations impacting the stream.

>>>>

  Previous studies have predominantly focused on the creation of gaps in stellar streams due to dark matter subhalo passages, with some exceptions that considered giant molecular clouds. If globular clusters can indeed create such gaps, this factor must be taken into account when using stellar streams to infer the population of dark matter subhaloes. In our study, we will fill this gap in the literature by simulating the creation of gaps in the Palomar 5~stream from the galactic globular clusters. We choose Palomar~5 since it is one of the most extensively studied and well-constrained globular cluster streams, known for its ease of observation. We present a result from one of our simulations in Fig. \ref{fig:stream_on_sky}. The following sections detail our modeling of the stream, its gravitational interactions with the galaxy and other globular clusters, and the statistical analysis of perturbations impacting the stream.
